### 2020-05-29 sc20_reviews/response.md

## Reviewer 1

  * Task graphs can be arbitrary, including irregular graphs. We added an example to Figure 1.

  * METG has already proven useful for exposing behaviors at the limits of system performance. We updated Section VI to provide additional details.

  * Our experiments are chosen to span the entire range of task granularities, from very efficient (large, and low overhead) to inefficient (small, and high overhead). METG naturally determines the point at which runtime overheads come to dominate application execution. What we report in the paper are empirical results: the limit of what each system can achieve. This is a lower bound, and generally, such systems will be efficient as long as tasks are at least that large. Also, as noted in the paper, clearly there are popular and widely used systems on both ends of this spectrum; therefore some classes of applications must be able to tolerate much larger task granularities.

  * For a specific example of an application where small task granularities are useful, see <https://ieeexplore.ieee.org/document/8948618>. Figure 2 shows that with a tile size of 1024 the algorithm achieves about 7 TFLOPS/s per GPU. The task executed on each tile is a straightforward matrix multiply, making it easy to determine the the FLOPS (and therefore task granularity): (2\*1024\*1024\*1024/10^9)/7000gflops = 307us.

@@

  * We renamed Section VI.

  * We added the Deakin citation to our related work.

## Reviewer 4

  * Task Bench provides access to a large space of behaviors (kernel computation, load imbalance, shape of the task graph, number of dependencies and their structure, amount of data communicated, etc.). We agree that there are dimensions of this space that are not currently covered by Task Bench, and that are covered by specific mini-apps; we consider this a good diretion for future work. In spite of this, the space covered by Task Bench today is already larger than the existing benchmarks, or any single mini-app. Moreover, Task Bench makes it dramatically easier to implement for a wide variety of systems, making comparative study feasible. We have added some clarifications to the introduction.

  * We updated the terminology in the introduction.

@@

  * We clarified the paragraph at the top of Section V-A.

  * We expanded Section VI.

## Reviewer 5

  * We agree that cross-validation with mini-apps is a good direction for future work, but that concrete benefits have already been demonstrated in the form of performance bugs found and fixed via Task Bench (see updated Section VI).

  * Whether dependencies are constructured ahead of time or on the fly is a feature of a specific implementation of Task Bench, not the core API. You can see in Listing 2 that the MPI implementation queries the core API to generate send and receive calls. Similar, these could be used to determine the set of tasks to issue (Dask, etc.) or the connectivity of the dataflow graph (TensorFlow, etc.). We ensure that all core APIs are very efficient, making these checks low-cost so that there is no penalty to querying the APIs on the fly (if that is how the programming model is designed to be used).

  * We added Section V-G.

  * Figure 11 is comparable to Figure 3. As described in the text, Figure 3 is generated from Figure 2 by computing, for each data point, efficiency and task granularity. These are derived metrics, resulting in a parametric graph. Intuitively, there is a data point per problem size, but task granularity does not necessarily decrease with problem size (due to runtime overheads and other factors). This view makes it intuitive how efficiency and task granularity are related.

  * We use MPS in the case of MPI with 4 ranks per GPU. Our code uses an offload model where any communicated data is copied to and from the GPU for each task execution. Using 4 ranks per node allows the copies to/from the GPU and kernel launches to be performed in parallel, increasing the utilization of the GPU (at the cost of higher overheads at small task granularities). All of these factors, including the kernel launch latency, are included in our task granularity measurements.

### 2020-06-01 1_introduction.tex
Tweak intro.
Apply Alex's edits.

The challenge of parallel and distributed computation has led to a
wide variety of proposals for programming models, languages, and
runtime systems. While these systems are well-represented in the literature, comprehensive and comparative performance evaluations
remain difficult to find. Our
goal in this paper is to develop a meaningful and useful framework for
comparing the performance of parallel and distributed programming
systems, to help users and developers evaluate the performance tradeoffs of these systems.

One approach to comparing performance is through \emph{proxy-} or
\emph{mini-apps}. Because they distill key computational characteristics of larger
applications, mini-apps offer insight
without the expense of developing production codes. However, despite the name, our experience is that
mini-apps still require significant investment to develop
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop a correct implementation. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Few published studies compare more than a handful of systems~\cite{LULESH13}.

@@

How does one predict whether performance will be good enough for a given application?
The most commonly reported metrics,
\emph{weak} and \emph{strong} scaling, do not directly characterize
the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from application costs
(such as communication) that scale with the number of nodes when
using progressively larger portions of a machine.

@@

We conduct a comprehensive study of all 15 Task Bench implementations on
up to 256 Haswell nodes of the Cori supercomputer~\cite{Cori}.
%% :
%% Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP, CUDA),
%% OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
%% PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
%% Spark \cite{Spark10}, StarPU \cite{StarPU11},
%% Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
%% X10 \cite{X1005}.
Using METG, we find that a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While some systems can achieve sub-microsecond METG(50\%) in
best-case scenarios, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. Our study includes several asynchronous systems
designed to provide benefits such as overlapped computation
and communication. While small-scale benchmarks of these systems
suffer from increased overhead, we find that the benefits of these systems become
tangible at scale (provided the runtime overhead doesn't increase
beyond about 100~\textmu{}s per task).

@@

Beyond comparative study, the ability to explore a large configuration
space also enables the discovery of bugs in the underlying systems. We
found five performance issues, ranging from communication efficiency
(Chapel, Realm), to the efficiency of task pruning, analysis and
constant folding (PaRSEC, Dask and TensorFlow). Three have been fixed
and all have been acknowledged by the developers of the respective
systems. (All were either fixed or worked around in our experiments.)
In some cases these correspond to order of magnitude (or even
asymptotic) improvements in the performance of the underlying
systems---benefits which apply well beyond Task Bench to all classes
of applications. The bugs are described in more detail in Section~\ref{sec:case-study}.

>>>>

The challenge of parallel and distributed computation has led to a
wide variety of proposals for programming models, languages, and
runtime systems. While these systems are well-represented in the literature, comprehensive and comparative performance evaluations
remain difficult to find. Our
goal in this paper is to develop a useful framework for
comparing the performance of parallel and distributed programming
systems, to help users and developers evaluate the performance tradeoffs of these systems.

{\color{blue}

Existing approaches to this problem focus on \emph{proxy-}/\emph{mini-apps}
or \emph{microbenchmarks}. These smaller codes distill key
computational characteristics of larger applications: mini-apps are
often derived from a larger code, and thus inherit some subset of its
properties, while benchmarks are typically chosen to reflect a more
narrow set of behaviors. In either case, while a variety of insight
can be gained, the overall programming effort required is proportional to the
product of the number of systems and behaviors being
evaluated. Few published studies compare more than a
handful of systems~\cite{LULESH13, Deakin19}.

}

\zap{
One approach to comparing performance is through \emph{proxy-} or
\emph{mini-apps}. Because they distill key computational characteristics of larger
applications, mini-apps offer insight
without the expense of developing production codes. However, despite the name, our experience is that
mini-apps still require significant investment to develop
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop a correct implementation. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Few published studies compare more than a handful of systems~\cite{LULESH13, Deakin19}.
} % zap

@@

How does one predict whether performance will be good enough for a given application?
The most commonly reported {\color{blue} measures},
\emph{weak} and \emph{strong} scaling, do not directly characterize
the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from application costs
(such as communication) that scale with the number of nodes when
using progressively larger portions of a machine.

@@

We conduct a comprehensive study of all 15 Task Bench implementations on
up to 256 Haswell nodes of the Cori supercomputer~\cite{Cori}.
%% :
%% Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP, CUDA),
%% OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
%% PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
%% Spark \cite{Spark10}, StarPU \cite{StarPU11},
%% Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
%% X10 \cite{X1005}.
Using METG, we find that a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in systems with the lowest
overheads. While some systems can achieve sub-microsecond METG(50\%) in
best-case scenarios, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. Our study includes several asynchronous systems
designed to provide benefits such as overlapped computation
and communication. While small-scale benchmarks of these systems
suffer from increased overhead, we find that the benefits of these systems become
tangible at scale (provided the runtime overhead doesn't increase
beyond about 100~\textmu{}s per task).

@@

Beyond comparative study, the ability to explore a large configuration
space also enables the discovery of bugs in the underlying systems. We
found five performance issues, ranging from communication efficiency
(Chapel, Realm), to the efficiency of task pruning, analysis and
constant folding (PaRSEC, Dask and TensorFlow). Three have been fixed
and all have been acknowledged by the developers of the respective
systems. (All were either fixed or worked around in our experiments.)
In some cases these correspond to order of magnitude or even
asymptotic improvements in the performance of the underlying
systems---benefits which apply well beyond Task Bench to all classes
of applications. The bugs are described in more detail in Section~\ref{sec:case-study}.

### 2020-06-01 2_task_bench.tex
Apply Alex's edits.

The Task Bench core library is fully validating. {\color{blue} The output of each
task is a tuple (time step, column) and is unique within a task
graph. All inputs are verified by checking the expected dependencies
against those received, and an assertion is thrown if validation
fails. These checks ensure that every execution of Task Bench is
correct. Note that the graph representation is concise, making these
checks very inexpensive.} An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

>>>>

The Task Bench core library is fully self-validating: {\color{blue} The output of each
task is a tuple $\langle \textrm{row, col}\rangle$ and is unique within a task
graph. All inputs are verified by checking the expected dependencies
against those received, and an assertion is thrown if validation
fails. These checks ensure that every execution of Task Bench is
correct. Note that the graph representation is concise, making these
checks very inexpensive.} An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

### 2020-06-01 4_metg.tex
Apply Alex's edits.

In Figure~\ref{fig:efficiency-mpi},
efficiency starts at 100\%. Initially task granularity
shrinks with minimal change in efficiency. As tasks shrink further, efficiency drops more rapidly, leading
to a vertical asymptote as overhead comes to dominate useful work.

@@

METG has a well-defined
relationship with quantities of interest such as
weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the weak and strong scaling of MPI Task Bench running a stencil pattern at a variety of problem sizes. In these
figures, the vertical axis is shown as wall time to emphasize the
relationship to time-to-solution, but it could equivalently be shown
as task granularity (as the number of tasks per execution is
fixed). Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to appear at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes
dominated by overhead. Note that the contours of the bottom of each
graph is identical and conforms to the METG curve (marked by the red,
dashed line).

>>>>

In Figure~\ref{fig:efficiency-mpi},
efficiency starts at 100\%. Initially task granularity
shrinks with minimal change in efficiency. As tasks shrink further, efficiency drops more rapidly, approaching a vertical asymptote as overhead comes to dominate useful work.

@@

METG has a well-defined
relationship with quantities of interest such as
weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the weak and strong scaling of MPI Task Bench running a stencil pattern at a variety of problem sizes. In these
figures, the vertical axis is shown as wall time to emphasize the
relationship to time-to-solution, but it could equivalently be shown
as task granularity (as the number of tasks per execution is
fixed). Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to appear at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes
dominated by overhead. Note that the contour of the bottom of each
graph is identical and conforms to the METG curve (marked by the red,
dashed line).

### 2020-06-01 5_evaluation.tex
Apply Alex's edits.

{\color{blue}
In order to ensure that all systems are properly configured, we
analyze the peak performance achieved by each. There should exist some
task granularity which is sufficient to offset the runtime overheads
of any system, regardless of how large those are. In practice, it's
best to verify this because system configuration can be unintuitive
and can lead to a loss in performance (e.g., due to not using all
available cores).
}

>>>>

{\color{blue}

We first consider the peak performance achieved by each system. There
should exist some task granularity which is sufficient to offset the
runtime overheads of any system, regardless of how large those
are. Even so, a variety of issues can lead to performance loss
(e.g. due to not using all available cores). Verifying that peak
performance is achieved ensures that there are no such flaws in our
configuration.

}
